---
title: "IRIDataMergedDataExploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
merged.data<-read.csv("cleaned_data_1427_1478_with_panelist_demographics.csv", header = TRUE, na.strings = c(".") )
merged.data$COUNT<-1
merged.data<-merged.data[,c(2:58)]
merged.data$PANID<-as.factor(merged.data$PANID)
merged.data$VEND<-as.factor(sprintf("%05d", merged.data$VEND))
merged.data$ITEM<-as.factor(sprintf("%05d", merged.data$ITEM))
merged.data$D<-as.factor(merged.data$D)
merged.data$PR<-as.factor(merged.data$PR)
# < 0.1, 0.1 < x < 0.26, 0.26 < x < 0.35, 0.35 < x < 0.3938, 0.3938 < x < 0.4894, 0.4894 < x < 0.675, 0.675+
merged.data$VOL_EQ<-cut(merged.data$VOL_EQ, breaks = c(-Inf, 0.1, 0.26, 0.35, 0.3938, 0.4894, 0.675, Inf), labels = c("MICRO", "VERY_SMALL", "SMALL", "MEDIUM_SMALL", "MEDIUM", "MEDIUM_LARGE", "LARGE"))
merged.data[c(22:57)]<-lapply(merged.data[c(22:57)], factor)

```

Lets see how many levels are in each of the factor columns:

```{r}
for (x in c(1:ncol(merged.data))) {
  if (is.factor(merged.data[,x])) {
    print(paste(colnames(merged.data)[x], "=", nlevels(merged.data[,x])))
  }
}
```
Should we reduce the number of brands we are dealing with?  Now its 29, maybe to 15?

```{r}
barplot(table(merged.data$VEND))
```
According to the bar chart we could reduce it to something like 6 or 7.


Lets do a barplot of some other interesting ones:

```{r}

barplot(table(merged.data$PRODUCT.TYPE))
```

We should probably get rid of everything but TOOTHEPASTE, could throw brand purchasing off.

```{r}
barplot(table(merged.data$VOL_EQ))
merged.data.regular<-merged.data[which(merged.data$SIZE == "REGULAR"),]
barplot(table(merged.data.regular$VOL_EQ))
```
```{r}
barplot(table(merged.data$SIZE))
```
Hmm, maybe only do one "SIZE", then divide that up into "VOL_EQ"s

```{r}
barplot(table(merged.data.regular$SIZE))
```


Lets look at for each person how many products in each brand type they purchased:

```{r}
brands.by.person<-aggregate(merged.data$COUNT, by=list(Person=merged.data$PANID, Brand=merged.data$VEND), FUN=sum)
brands.by.person<-brands.by.person[order(brands.by.person$Person),]
brands.by.person
```
How about number of brands a each person switched between:

```{r}
brand.per.person<-aggregate(brands.by.person$x, by=list(Person=brands.by.person$Person), FUN=sum)
brand.per.person

hist(brand.per.person$x)
```

