---
title: "IRIDataMergedDataExploration"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
merged.data<-read.csv("cleaned_data_1427_1478_with_panelist_demographics.csv", header = TRUE, na.strings = c(".") )
merged.data$COUNT<-1
merged.data<-merged.data[,c(2:58)]
merged.data$PANID<-as.factor(merged.data$PANID)
merged.data$VEND<-as.factor(sprintf("%05d", merged.data$VEND))
merged.data$ITEM<-as.factor(sprintf("%05d", merged.data$ITEM))
merged.data$D<-as.factor(merged.data$D)
merged.data$PR<-as.factor(merged.data$PR)
# < 0.1, 0.1 < x < 0.26, 0.26 < x < 0.35, 0.35 < x < 0.3938, 0.3938 < x < 0.4894, 0.4894 < x < 0.675, 0.675+
merged.data$VOL_EQ<-cut(merged.data$VOL_EQ, breaks = c(-Inf, 0.1, 0.26, 0.35, 0.3938, 0.4894, 0.675, Inf), labels = c("MICRO", "VERY_SMALL", "SMALL", "MEDIUM_SMALL", "MEDIUM", "MEDIUM_LARGE", "LARGE"))
merged.data[c(22:57)]<-lapply(merged.data[c(22:57)], factor)

```

Number of panelists:
```{r}
nlevels(merged.data$PANID)
```

Number of transactions:
```{r}
nrow(merged.data)
```

Average purchases per person:
```{r}
nrow(merged.data) / nlevels(merged.data$PANID)

```


Lets see how many levels are in each of the factor columns:

```{r}
for (x in c(1:ncol(merged.data))) {
  if (is.factor(merged.data[,x])) {
    print(paste(colnames(merged.data)[x], "=", nlevels(merged.data[,x])))
  }
}
```


Should we reduce the number of brands we are dealing with?  Now its 29, maybe to 10?

```{r}
barplot(table(merged.data$VEND))
```
According to the bar chart we could reduce it to something like 6 or 7.

Find out which ones they are:

```{r}
vendor.counts<-aggregate(merged.data$COUNT, by=list(Brand<-merged.data$VEND), FUN=sum)
head(vendor.counts[order(-vendor.counts$x),], n = 10)
#lets take anything above 30
brands<-vendor.counts[which(vendor.counts$x > 31),1]
brands
# now remove all non-brand from data
merged.data.reduced<-merged.data[which(merged.data$VEND %in% brands),]
# how to reduce number of levels to match new?
merged.data.reduced$VEND<-factor(merged.data.reduced$VEND)
levels(merged.data.reduced$VEND)
```


Lets do a barplot of some other interesting ones:

```{r}

barplot(table(merged.data.reduced$PRODUCT.TYPE))
```

We should probably get rid of everything but TOOTHEPASTE, could throw brand purchasing off.
```{r}
merged.data.reduced<-merged.data.reduced[which(merged.data.reduced$PRODUCT.TYPE == "TOOTHPASTE"),]
aggregate(merged.data.reduced$COUNT, by=list(PRODUCT.TYPES=merged.data.reduced$PRODUCT.TYPE), FUN=sum)
merged.data.reduced$PRODUCT.TYPE<-factor(merged.data.reduced$PRODUCT.TYPE)
# we should be able to just get rid of this column now
levels(merged.data.reduced$PRODUCT.TYPE)
```



```{r}
barplot(table(merged.data$SIZE))
```


Hmm, maybe only do one "SIZE", then divide that up into "VOL_EQ"s


```{r}
merged.data.reduced<-merged.data.reduced[which(merged.data.reduced$SIZE == "REGULAR"),]
merged.data.reduced$SIZE<-factor(merged.data.reduced$SIZE)
levels(merged.data.reduced$SIZE)
# we should be able to just get rid of this column now
barplot(table(merged.data.reduced$VOL_EQ))
```

Maybe get rid of MICRO and LARGE?

Lets look at purchases per person:

```{r}
purchases.per.person<-aggregate(merged.data.reduced$COUNT, by=list(Person=merged.data.reduced$PANID), FUN=sum)

barplot(table(as.factor(purchases.per.person$x)))

```

Hmm, there are a lot of people that only made 1 purchase.  Thats ok I guess.

Lets get an average number of purchases a person made:

```{r}
mean(aggregate(merged.data.reduced$COUNT, by=list(Person=merged.data.reduced$PANID), FUN=sum)$x)

```



Lets look at for each person how many products in each brand type they purchased:

```{r}
brands.by.person<-aggregate(merged.data.reduced$COUNT, by=list(Person=merged.data.reduced$PANID, Brand=merged.data.reduced$VEND), FUN=sum)
brands.by.person<-brands.by.person[order(brands.by.person$Person),]
head(brands.by.person)
```

How about number of brands a each person switched between:

```{r}
brands.by.person$COUNT<-1
brand.per.person<-aggregate(brands.by.person$COUNT, by=list(Person=brands.by.person$Person), FUN=sum)
brand.per.person$x<-as.factor(brand.per.person$x)

barplot(table(brand.per.person$x))
```
Shows that decent number of people switched between a few brands, but not many above 3.

Compute brand loyalty:

Equation used: BL3 := Total purchase level of brand i by household n during the whole time period / Total purchase level of the product category by household n during the whole time period.

```{r}
purchases.by.brand.per.household<-aggregate(merged.data.reduced$COUNT, by=list(Brand=merged.data.reduced$VEND, Household=merged.data.reduced$PANID), FUN=sum)
total.purchases.per.household<-aggregate(purchases.by.brand.per.household$x, by=list(Household=purchases.by.brand.per.household$Household), FUN=sum)

purchases.by.brand.per.household$loyalty<-0
for (idx in c(1:nrow(purchases.by.brand.per.household))) {
  house<-purchases.by.brand.per.household[idx,2]
  total<-total.purchases.per.household[which(total.purchases.per.household[,1] == house),2]
  purchases.by.brand.per.household[idx,4]<-purchases.by.brand.per.household$x[idx] / total
}

merged.data.reduced$LOYALTY<-0
for (idx in c(1:nrow(merged.data.reduced))) {
  brand<-merged.data.reduced$VEND[idx]
  house<-merged.data.reduced$PANID[idx]
  loyalty<-purchases.by.brand.per.household[which(purchases.by.brand.per.household$Household == house & purchases.by.brand.per.household$Brand == brand),]$loyalty
  merged.data.reduced$LOYALTY[idx]<-loyalty
}

hist(merged.data.reduced$LOYALTY)
```


```{r}

for (x in c(2:ncol(merged.data.reduced))) {
  if (is.factor(merged.data.reduced[,x])) {
    merged.data.reduced[,x]<-factor(merged.data.reduced[,x])
    barplot(table(merged.data.reduced[x]), main = colnames(merged.data.reduced)[x])
  }
}

# a lot of "MISSING" values on the COLOR plot, ignore for now

```



```{r}
for (x in c(1:ncol(merged.data.reduced))) {
  if (is.factor(merged.data.reduced[,x])) {
    print(paste(colnames(merged.data.reduced)[x], "=", nlevels(merged.data.reduced[,x])))
  }
}

```

We can get rid of all the columns that have a only 1 factor:
"Microwave.Owned.by.HH = 1"
"EXT_FACT = 1"
"STORE.LOCATION = 1"
"PRODUCT.TYPE = 1"
"SIZE = 1"

```{r}
cnames<-colnames(merged.data.reduced)
cols.remove<-c(which(cnames == "Microwave.Owned.by.HH"),
  which(cnames == "EXT_FACT"),
  which(cnames == "STORE.LOCATION"),
  which(cnames == "PRODUCT.TYPE"),
  which(cnames == "SIZE"),
  which(cnames == "COUNT"),
  which(cnames == "VENDORITEMCOUNT"))

merged.data.reduced<-merged.data.reduced[,-cols.remove]

for (x in c(1:ncol(merged.data.reduced))) {
  if (is.factor(merged.data.reduced[,x])) {
    print(paste(colnames(merged.data.reduced)[x], "=", nlevels(merged.data.reduced[,x])))
  }
}

```

To work with these utility function GAM models and mlogit models we need to create some alternative specific dummies.  Here is the code to do that. It creates a column for each brand alternate and puts a 1 in the column for the brand chosen for the row.

```{r}
merged.data.reduced.dummies<-merged.data.reduced
#For every unique value in the string column, create a new 1/0 column
#This is what Factors do "under-the-hood" automatically when passed to function requiring numeric data
for(level in unique(merged.data.reduced.dummies$VEND)){
  merged.data.reduced.dummies[paste("brand", level, sep = "_")] <- ifelse(merged.data.reduced.dummies$VEND == level, 1, 0)
}

merged.data.reduced.dummies
```

Number sold of each item:

```{r}
temp<-merged.data.reduced
temp$COUNT<-1
num.item.sold<-aggregate(temp$COUNT, by=list(Item=temp$ITEM), FUN=sum)
num.item.sold[order(-num.item.sold$x),]
hist(num.item.sold$x)

nrow(num.item.sold[which(num.item.sold$x > 50),])
```



We can try a GAM utility function model with the merged.data.reduced.dummies data:

```{r}

```



Or a multinomial logit model with the merged.data.reduce data:

```{r}
library("mlogit")

head(merged.data.reduced)

# I don't think I'm understanding this so lets reduce our number of vars to make it easier
merged.data.reduced.test<-merged.data.reduced[,c(1, 2, 5, 6, 7, 8, 9, 10, 11, 12)]

merged.data.reduced.test

# Hmm, the varyiables that are "alternative specific" are actually specific to the ITEM not the VEND/Brand.  So I think we need our "choices" to be on items?  
# right now we have 328 items


alevels<-c(levels(merged.data.reduced$VEND))
cvars<-c(colnames(merged.data.reduced)[c(16:49)])
vnames<-c(colnames(merged.data.reduced)[c(3:15)])
# I don't think this is correct yet
transformed.data<-mlogit.data(merged.data.reduced, shape = "wide", varying = 3:15, v.names=vnames, choice = "VEND", alt.levels = alevels, id.var = "PANID")

transformed.data

```

