---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plyr)
library(dplyr)

require(utils)
library(zoo)
library(mgcv)
library(mlogit)

```



```{r}
trimspaces <- function(dat) {
  dat$COLUPC<-trimws(dat$COLUPC)
  dat$WEEK<-trimws(dat$WEEK)
  dat$IRI_KEY<-trimws(dat$IRI_KEY)
  return (dat)
}

combineupc <- function(dat) {
  dat$COLUPC<-paste(sprintf("%02d", dat$SY), dat$GE, sprintf("%05d", dat$VEND), sprintf("%05d", dat$ITEM), sep="")
  return (dat)
}
```



```{r}
panel.dk = read.table("data/toothpa_PANEL_DR_1427_1478.DAT", sep="", header = TRUE, na.strings="", stringsAsFactors = F, colClasses = c(rep("character",4),"numeric", "character", "character")) 
panel.dk<-trimspaces(panel.dk)
panel.gk = read.table("data/toothpa_PANEL_GR_1427_1478.DAT", sep="", header = TRUE, na.strings="", stringsAsFactors = F, colClasses = c(rep("character",4),"numeric", "character", "character"))
panel.gk<-trimspaces(panel.gk)
panel.mk = read.table("data/toothpa_PANEL_MA_1427_1478.DAT", sep="", header = TRUE, na.strings="", stringsAsFactors = F, colClasses = c(rep("character",4),"numeric", "character", "character"))
panel.mk<-trimspaces(panel.mk)

panel.all<-rbind(panel.dk, panel.gk, panel.mk)
```


```{r}
trans.groc = read.table("data/toothpa_groc_1427_1478", sep="", header = TRUE, na.strings="", stringsAsFactors = F, colClasses = c(rep("character",2),rep("numeric", 6), "character", "numeric", "numeric"))
trans.groc<-combineupc(trans.groc)
trans.groc<-trimspaces(trans.groc)

trans.drug = read.table("data/toothpa_drug_1427_1478", sep="", header = TRUE, na.strings="", stringsAsFactors = F, colClasses = c(rep("character",2),rep("numeric", 6), "character", "numeric", "numeric"))
trans.drug<-combineupc(trans.drug)
trans.drug<-trimspaces(trans.drug)

trans.all<-rbind(trans.groc, trans.drug)
```


```{r}
prod.attr = read.csv("toothpa_prod_attr.csv", header = TRUE)
prod.attr$COLUPC<-paste(sprintf("%02d", prod.attr$SY), prod.attr$GE, sprintf("%05d", prod.attr$VEND), sprintf("%05d", prod.attr$ITEM), sep="")
```


```{r}
joined.one<-merge(x=panel.all, y=trans.all, by=c("COLUPC", "IRI_KEY", "WEEK"))
joined.all<-merge(joined.one, prod.attr, by=c("COLUPC"))
```

```{r}
levels(joined.all$SIZE)[8]<-"REGULAR"

reduced.data<-data.frame(PANID=as.factor(joined.all$PANID), 
                         UNITS=as.double(joined.all$UNITS.x), 
                         OUTLET=as.factor(joined.all$OUTLET), 
                         DOLLARS=as.double(joined.all$DOLLARS.x),
                         WEEK=as.double(joined.all$WEEK),
                         VEND=as.factor(joined.all$VEND.x), 
                         ITEM=as.factor(joined.all$ITEM.x), 
                         FEATURE=as.factor(joined.all$F), 
                         DISPLAY=joined.all$D, 
                         PRICEREDUCTION=joined.all$PR, 
                         VOL_EQ=joined.all$VOL_EQ, 
                         SIZE=joined.all$SIZE,
#                         FLAVOR.SCENT=joined.all$FLAVOR.SCENT, 
#                         FORM=joined.all$FORM, 
#                         PACKAGE=joined.all$PACKAGE, 
                         PRODUCT.TYPE=joined.all$PRODUCT.TYPE 
#                         TYPE.OF.FORMULAT=joined.all$TYPE.OF.FORMULA
                         )
reduced.data$FEATURE <- as.character(reduced.data$FEATURE)
reduced.data[reduced.data$FEATURE == "NONE",]$FEATURE <- "0"
reduced.data[reduced.data$FEATURE == "C",]$FEATURE <- "1"
reduced.data[reduced.data$FEATURE == "B",]$FEATURE <- "2"
reduced.data[reduced.data$FEATURE == "A",]$FEATURE <- "3"
reduced.data[reduced.data$FEATURE == "A+",]$FEATURE <- "4"
```


```{r}
reduced.data$COUNT<-1

reduced.data<-reduced.data[which(reduced.data$PRODUCT.TYPE == "TOOTHPASTE"),]
reduced.data$PRODUCT.TYPE<-factor(reduced.data$PRODUCT.TYPE)

reduced.data<-reduced.data[which(reduced.data$SIZE == "REGULAR"),]
reduced.data$SIZE<-factor(reduced.data$SIZE)

#get rid of size and product type now
cnames<-colnames(reduced.data)
cols.remove<-c(which(cnames == "SIZE"), which(cnames == "PRODUCT.TYPE"))
reduced.data<-reduced.data[,-cols.remove]

vendor.counts<-aggregate(reduced.data$COUNT, by=list(Brand<-reduced.data$VEND), FUN=sum)
#lets take anything above 40
brands<-as.character(vendor.counts[which(vendor.counts$x > 40),1])
# 
# reduced.data<-reduced.data[which(reduced.data$VEND %in% brands),]
# reduced.data$VEND<-factor(reduced.data$VEND)

```

```{r}
purchases.by.brand.per.household<-aggregate(reduced.data$COUNT, by=list(Brand=reduced.data$VEND, Household=reduced.data$PANID), FUN=sum)
total.purchases.per.household<-aggregate(purchases.by.brand.per.household$x, by=list(Household=purchases.by.brand.per.household$Household), FUN=sum)

purchases.by.brand.per.household$loyalty<-0
for (idx in c(1:nrow(purchases.by.brand.per.household))) {
  house<-purchases.by.brand.per.household[idx,2]
  total<-total.purchases.per.household[which(total.purchases.per.household[,1] == house),2]
  purchases.by.brand.per.household[idx,4]<-purchases.by.brand.per.household$x[idx] / total
}

reduced.data$LOYALTY<-0
for (idx in c(1:nrow(reduced.data))) {
  brand<-reduced.data$VEND[idx]
  house<-reduced.data$PANID[idx]
  loyalty<-purchases.by.brand.per.household[which(purchases.by.brand.per.household$Household == house & purchases.by.brand.per.household$Brand == brand),]$loyalty
  reduced.data$LOYALTY[idx]<-loyalty
}

hist(reduced.data$LOYALTY)
barplot(table(reduced.data$VOL_EQ))

```
```{r}
summary(joined.all)
hist(reduced.data$FEATURE)

reduced.data$FEATURE <- as.numeric(reduced.data$FEATURE)
reduce.feature<-aggregate(reduced.data$FEATURE, by=list(VEND=reduced.data$VEND, WEEK=reduced.data$WEEK), FUN=max)
#reduce.display[which(reduce.display$x > 0),3]<-1

hist(reduce.feature$x)

reduced.data$FEATURE<-NA
# now replace all the DISPLAY values in our dataset with the weekly avereage for the vendor
for (idx in c(1:nrow(reduced.data))) {
  brand<-reduced.data$VEND[idx]
  week<-reduced.data$WEEK[idx]
  av.feature<-reduce.feature[which(reduce.feature$WEEK == week & reduce.feature$VEND == brand),]$x
  reduced.data$FEATURE[idx]<-av.feature
}

# shows that comparitively not many individual items had a display, but usually at least one item from a particular brand had a display
hist(reduced.data$FEATURE)
```
```


```{r}

summary(joined.all)
hist(reduced.data$DISPLAY)

reduce.display<-aggregate(reduced.data$DISPLAY, by=list(VEND=reduced.data$VEND, WEEK=reduced.data$WEEK), FUN=max)
#reduce.display[which(reduce.display$x > 0),3]<-1

hist(reduce.display$x)

reduced.data$DISPLAY<-NA
# now replace all the DISPLAY values in our dataset with the weekly avereage for the vendor
for (idx in c(1:nrow(reduced.data))) {
  brand<-reduced.data$VEND[idx]
  week<-reduced.data$WEEK[idx]
  av.display<-reduce.display[which(reduce.display$WEEK == week & reduce.display$VEND == brand),]$x
  reduced.data$DISPLAY[idx]<-av.display
}

# shows that comparitively not many individual items had a display, but usually at least one item from a particular brand had a display
hist(reduced.data$DISPLAY)


hist(reduced.data$PRICEREDUCTION)

reduce.pr<-aggregate(reduced.data$PRICEREDUCTION, by=list(VEND=reduced.data$VEND, WEEK=reduced.data$WEEK), FUN=sum)
reduce.pr[which(reduce.pr$x > 0),3]<-1

reduced.data$PRICEREDUCTION<-NA
for (idx in c(1:nrow(reduced.data))) {
  brand<-reduced.data$VEND[idx]
  week<-reduced.data$WEEK[idx]
  av.pr<-reduce.pr[which(reduce.pr$WEEK == week & reduce.pr$VEND == brand),]$x
  reduced.data$PRICEREDUCTION[idx]<-av.pr
}

# same with price reduction
hist(reduced.data$PRICEREDUCTION)
```


```{r}
# PRICE
reduced.data$PRICE_PER_OUNCE<-(reduced.data$DOLLARS/reduced.data$UNITS) / reduced.data$VOL_EQ
tpriceDf <- reduced.data %>% group_by(WEEK, VEND) %>% dplyr::summarise(AVGRATE = mean(PRICE_PER_OUNCE))

priceDf <- expand.grid(WEEK=c(min(tpriceDf$WEEK) : max(tpriceDf$WEEK)), VEND = unique(reduced.data$VEND))

priceDf <- merge(x=priceDf, y=tpriceDf, by=c("WEEK", "VEND"), all.x=TRUE)

priceDf <- priceDf[order(priceDf$VEND, priceDf$WEEK),]

for(i in unique(priceDf$VEND)){
  if(is.na(priceDf[priceDf$WEEK == 1427 &
             priceDf$VEND == i,]$AVGRATE)){
    tdf <- priceDf[priceDf$VEND == i &
                     !is.na(priceDf$AVGRATE),]
    priceDf[priceDf$WEEK == 1427 &
              priceDf$VEND == i,]$AVGRATE <- tdf[order(tdf$VEND),]$AVGRATE[1]
  }
}

#priceDf[which(priceDf$WEEK == 1427 & priceDf$VEND == 24291),3]<-7.92

priceDf <- priceDf %>%
  group_by(VEND) %>% 
  mutate(AVGRATE = na.locf(AVGRATE, na.rm = T))

choicePriceDf <- priceDf[priceDf$VEND %in% brands,]
noChoicePriceDf <- priceDf[!priceDf$VEND %in% brands,]
noChoicePriceDf <- noChoicePriceDf %>%
  group_by(WEEK) %>%
  dplyr::summarise(AVGRATE = mean(AVGRATE))
noChoicePriceDf$VEND <- "0"
choicePriceDf$VEND <- as.character(choicePriceDf$VEND)
noChoicePriceDf <- noChoicePriceDf[,c(1,3,2)]
choicePriceDf <- data.frame(choicePriceDf[,c(1,2,3)])

priceDf <- rbind(choicePriceDf, noChoicePriceDf)


```

```{r}
# DISPLAY
priceDfDisplay <- expand.grid(WEEK=c(min(reduced.data$WEEK) : max(reduced.data$WEEK)), VEND = unique(reduced.data$VEND))
disp.data <- unique(reduced.data[,c(5, 6, 9)])
priceDfDisplay <- unique(merge(x=priceDfDisplay, y=disp.data, by=c("WEEK", "VEND"), all.x=TRUE))

priceDfDisplay <- priceDfDisplay[order(priceDfDisplay$VEND, priceDfDisplay$WEEK),]
priceDfDisplay[is.na(priceDfDisplay$DISPLAY),]$DISPLAY <- 0

# 
# priceDfDisplay[which(priceDfDisplay$WEEK == 1427 & priceDfDisplay$VEND == 24291),3]<-0
# 
# priceDfDisplay[which(priceDfDisplay$VEND == 24291),]
# 
# priceDfDisplay <- priceDfDisplay %>%
#   group_by(VEND) %>% 
#   mutate(DISPLAY = na.locf(DISPLAY, na.rm = T))
# 
# priceDfDisplay[which(priceDfDisplay$VEND == 24291),]
priceDfDisplay$DISPLAY <- as.numeric(priceDfDisplay$DISPLAY)
choicePriceDfDisplay <- priceDfDisplay[priceDfDisplay$VEND %in% brands,]
noChoicePriceDfDisplay <- priceDfDisplay[!priceDfDisplay$VEND %in% brands,]

noChoicePriceDfDisplay <- noChoicePriceDfDisplay %>%
  group_by(WEEK) %>%
  dplyr::summarise(DISPLAY = max(DISPLAY))
noChoicePriceDfDisplay$VEND <- "0"
choicePriceDfDisplay$VEND <- as.character(choicePriceDfDisplay$VEND)
noChoicePriceDfDisplay <- noChoicePriceDfDisplay[,c(1,3,2)]
choicePriceDfDisplay <- data.frame(choicePriceDfDisplay[,c(1,2,3)])

priceDfDisplay <- rbind(choicePriceDfDisplay, noChoicePriceDfDisplay)

priceDfDisplay$DISPLAY <- as.numeric(priceDfDisplay$DISPLAY)

```

```{r}
# FEATURE
priceDfFeature <- expand.grid(WEEK=c(min(reduced.data$WEEK) : max(reduced.data$WEEK)), VEND = unique(reduced.data$VEND))
feature.data <- unique(reduced.data[,c(5, 6, 8)])
priceDfFeature <- unique(merge(x=priceDfFeature, y=feature.data, by=c("WEEK", "VEND"), all.x=TRUE))

priceDfFeature <- priceDfFeature[order(priceDfFeature$VEND, priceDfFeature$WEEK),]
priceDfFeature[is.na(priceDfFeature$FEATURE),]$FEATURE <- 0

# 
# priceDfDisplay[which(priceDfDisplay$WEEK == 1427 & priceDfDisplay$VEND == 24291),3]<-0
# 
# priceDfDisplay[which(priceDfDisplay$VEND == 24291),]
# 
# priceDfDisplay <- priceDfDisplay %>%
#   group_by(VEND) %>% 
#   mutate(DISPLAY = na.locf(DISPLAY, na.rm = T))
# 
# priceDfDisplay[which(priceDfDisplay$VEND == 24291),]
priceDfFeature$FEATURE <- as.numeric(priceDfFeature$FEATURE)
choicePriceDfFeature <- priceDfFeature[priceDfFeature$VEND %in% brands,]
noChoicePriceDfFeature <- priceDfFeature[!priceDfFeature$VEND %in% brands,]

noChoicePriceDfFeature <- noChoicePriceDfFeature %>%
  group_by(WEEK) %>%
  dplyr::summarise(FEATURE = max(FEATURE))
noChoicePriceDfFeature$VEND <- "0"
choicePriceDfFeature$VEND <- as.character(choicePriceDfFeature$VEND)
noChoicePriceDfFeature <- noChoicePriceDfFeature[,c(1,3,2)]
choicePriceDfFeature <- data.frame(choicePriceDfFeature[,c(1,2,3)])

priceDfFeature <- rbind(choicePriceDfFeature, noChoicePriceDfFeature)

priceDfFeature$FEATURE <- as.numeric(priceDfFeature$FEATURE)

```

```{r}
# PRICEREDUCTION
priceDfPR <- expand.grid(WEEK=c(min(reduced.data$WEEK) : max(reduced.data$WEEK)), VEND = unique(reduced.data$VEND))
pr.data <- unique(reduced.data[,c(5, 6, 10)])
priceDfPR <- merge(x=priceDfPR, y=pr.data, by=c("WEEK", "VEND"), all.x=TRUE)


priceDfPR <- priceDfPR[order(priceDfPR$VEND, priceDfPR$WEEK),]
priceDfPR[is.na(priceDfPR$PRICEREDUCTION),]$PRICEREDUCTION <- 0

# priceDfPR[which(priceDfPR$WEEK == 1427 & priceDfPR$VEND == 24291),3]<-0
# 
# priceDfPR[which(priceDfPR$VEND == 24291),]
# 
# priceDfPR <- priceDfPR %>%
#   group_by(VEND) %>% 
#   mutate(PRICEREDUCTION = na.locf(PRICEREDUCTION, na.rm = T))
# 
# priceDfPR[which(priceDfPR$VEND == 24291),]

priceDfPR$PRICEREDUCTION <- as.logical(priceDfPR$PRICEREDUCTION)
choicePriceDfPR <- priceDfPR[priceDfPR$VEND %in% brands,]
noChoicePriceDfPR <- priceDfPR[!priceDfPR$VEND %in% brands,]

noChoicePriceDfPR <- noChoicePriceDfPR %>%
  group_by(WEEK) %>%
  dplyr::summarise(PRICEREDUCTION = any(PRICEREDUCTION))
noChoicePriceDfPR$VEND <- "0"
choicePriceDfPR$VEND <- as.character(choicePriceDfPR$VEND)
noChoicePriceDfPR <- noChoicePriceDfPR[,c(1,3,2)]
choicePriceDfPR <- data.frame(choicePriceDfPR[,c(1,2,3)])

priceDfPR <- rbind(choicePriceDfPR, noChoicePriceDfPR)

priceDfPR$PRICEREDUCTION <- as.numeric(priceDfPR$PRICEREDUCTION)

```


```{r}
combined<-merge(x = merge(x=merge(x=priceDf, y=priceDfDisplay, by=c("WEEK", "VEND"), all.x=TRUE), y=priceDfPR, by=c("WEEK", "VEND"), all.x=TRUE), y = priceDfFeature, all.x=TRUE)
```

```{r}

panelist.attrs = read.csv("data/DEMOS_1322_1373.csv", header = TRUE)
names(panelist.attrs)[1]<-"PANID"
reduced.data.test<-merge(reduced.data, panelist.attrs, by=c("PANID"))

panelist.attrs$MALE_SMOKE[which(panelist.attrs$MALE_SMOKE == ".")]<-0
panelist.attrs$FEM_SMOKE[which(panelist.attrs$FEM_SMOKE == ".")]<-0
panelist.attrs$MALE_SMOKE <- as.numeric(as.character(panelist.attrs$MALE_SMOKE))
panelist.attrs$FEM_SMOKE <- as.numeric(as.character(panelist.attrs$FEM_SMOKE))

attrs.reduced<-panelist.attrs[,c(1, 3, 15, 20)]
panelists<-reduced.data[,c(1, 5)]
panelists.with.income<-merge(x=panelists, y=attrs.reduced, by=c("PANID"), all.x = TRUE)

data.subset<-reduced.data[,c(1, 6, 13)]
panelists.from.trans<-unique(data.subset$PANID)
panelists.with.income<-panelists.with.income[which(panelists.with.income$PANID %in% panelists.from.trans),]

getLoyaltyByPanelistVendor <- function(vendor, panelist){
  return (data.subset[data.subset$VEND == vendor &
                                        data.subset$PANID == panelist,]$LOYALTY[1])
}


for(i in brands){
  param <- paste("LOYALTY", i, sep=".")
  panelists.with.income[,param] <- sapply(1:nrow(panelists.with.income), function(x) {getLoyaltyByPanelistVendor(vendor = i, panelist = panelists.with.income[x,]$PANID)})
}

noChoiceLoyalty <- data.frame(PANID = panelists.with.income$PANID)
for(i in unique(reduced.data[!reduced.data$VEND %in% brands,]$VEND)){
  param <- paste("LOYALTY", i, sep=".")
  noChoiceLoyalty[,param] <- sapply(1:nrow(panelists.with.income), function(x) {getLoyaltyByPanelistVendor(vendor = i, panelist = panelists.with.income[x,]$PANID)})
}
noChoiceLoyalty[is.na(noChoiceLoyalty)] <- 0
noChoiceLoyalty$max <- apply(noChoiceLoyalty[,-1], 1, max)

panelists.with.income$LOYALTY.0 <- sapply(1:nrow(panelists.with.income), function(x) {return(noChoiceLoyalty[noChoiceLoyalty$PANID == panelists.with.income[x,]$PANID,]$max[1])})

test<-panelists.with.income
test[is.na(test)]<-0
```

```{r}

for(level in brands){
  reduced.data[paste("brand", level, sep = "_")] <- ifelse(reduced.data$VEND == level, 1, 0)
}

brand.dummies.data<-reduced.data[,c(1, 5, 14:20)]
test$WEEK<-as.factor(test$WEEK)
test$PANID<-as.factor(test$PANID)

brand.dummies.data$WEEK<-as.factor(brand.dummies.data$WEEK)
brand.dummies.data$PANID<-as.factor(brand.dummies.data$PANID)

all.data.combined<-merge(x=brand.dummies.data, y=test, by=c("PANID", "WEEK"), all.x=TRUE)

all.data.combined
```

```{r}

getVendParamByWeek <- function(vendor, week, param, value){
  param <- 
  return(combined[combined$VEND == vendor &
                  combined$WEEK == week,param][1])
}

for(i in unique(combined$VEND)){
  avgRateParam <- paste("AVGRATE", i, sep=".")
  displayParam <- paste("DISPLAY", i, sep=".")
  pricereductionParam <- paste("PRICEREDUCTION", i, sep=".")
  featureParam <- paste("FEATURE", i, sep=".")
  all.data.combined[,avgRateParam] <- sapply(1:nrow(all.data.combined), function(x) { getVendParamByWeek(vendor = i, week = all.data.combined[x,]$WEEK, param = "AVGRATE")})
  all.data.combined[,displayParam] <- sapply(1:nrow(all.data.combined), function(x) { getVendParamByWeek(vendor = i, week = all.data.combined[x,]$WEEK, param = "DISPLAY")})
  all.data.combined[,pricereductionParam] <- sapply(1:nrow(all.data.combined), function(x) { getVendParamByWeek(vendor = i, week = all.data.combined[x,]$WEEK, param = "PRICEREDUCTION")})
  all.data.combined[,featureParam] <- sapply(1:nrow(all.data.combined), function(x) { getVendParamByWeek(vendor = i, week = all.data.combined[x,]$WEEK, param = "FEATURE")})
}
  

all.data.combined$PRICE_PER_OUNCE <- NULL

all.data.combined$choice <- paste(all.data.combined$brand_10158, all.data.combined$brand_33200, all.data.combined$brand_35000, all.data.combined$brand_37000, all.data.combined$brand_53100, all.data.combined$brand_77326, sep="")

all.data.combined$choiceLabel <- "0"
all.data.combined[all.data.combined$choice == "000000",]$choiceLabel <- "0"
all.data.combined[all.data.combined$choice == "100000",]$choiceLabel <- "10158"
all.data.combined[all.data.combined$choice == "010000",]$choiceLabel <- "33200"
all.data.combined[all.data.combined$choice == "001000",]$choiceLabel <- "35000"
all.data.combined[all.data.combined$choice == "000100",]$choiceLabel <- "37000"
all.data.combined[all.data.combined$choice == "000010",]$choiceLabel <- "53100"
all.data.combined[all.data.combined$choice == "000001",]$choiceLabel <- "77326"

all.data.combined[all.data.combined$choice == "000000",]$choice <- 0
all.data.combined[all.data.combined$choice == "100000",]$choice <- 1
all.data.combined[all.data.combined$choice == "010000",]$choice <- 2
all.data.combined[all.data.combined$choice == "001000",]$choice <- 3
all.data.combined[all.data.combined$choice == "000100",]$choice <- 4
all.data.combined[all.data.combined$choice == "000010",]$choice <- 5
all.data.combined[all.data.combined$choice == "000001",]$choice <- 6

all.data.combined$choice <- as.numeric(all.data.combined$choice)
write.csv(all.data.combined, file="finaldata.csv")


finaldata <- unique(all.data.combined)

finaldata$WEEK <- as.numeric(as.character(finaldata$WEEK))


mnlmodel <- gam(list(choice~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK + LOYALTY.10158 + AVGRATE.10158 +  DISPLAY.10158 + FEATURE.10158,  ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK +  LOYALTY.33200 + AVGRATE.33200 + DISPLAY.33200 + FEATURE.33200, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK + LOYALTY.35000 + AVGRATE.35000 + DISPLAY.35000 + FEATURE.35000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK + LOYALTY.37000 + AVGRATE.37000 + DISPLAY.37000 + FEATURE.37000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK + LOYALTY.53100 + AVGRATE.53100 + DISPLAY.53100 + FEATURE.53100, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE +  WEEK + LOYALTY.77326 + AVGRATE.77326 + DISPLAY.77326 + FEATURE.77326), data=finaldata, family=multinom(K=6))

gamWeekLoyaltyPriceDplyModel <- gam(list(choice~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.10158, AVGRATE.10158, by=DISPLAY.10158)+ FEATURE.10158,  ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) +  s(LOYALTY.33200,  AVGRATE.33200, by= DISPLAY.33200) + FEATURE.33200, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.35000, AVGRATE.35000, by=DISPLAY.35000)  + FEATURE.35000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + WEEK + s(LOYALTY.37000, AVGRATE.37000, by=DISPLAY.37000) + FEATURE.37000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.53100,  AVGRATE.53100, by=DISPLAY.53100) + FEATURE.53100, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE +  s(WEEK) + s(LOYALTY.77326, AVGRATE.77326, by=DISPLAY.77326) + FEATURE.77326), data=finaldata, family=multinom(K=6))

gamWeekPriceLoyaltyModel <- gam(list(choice~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.10158) + s(AVGRATE.10158) +  DISPLAY.10158 +  PRICEREDUCTION.10158,  ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) +  s(LOYALTY.33200) + s(AVGRATE.33200) + DISPLAY.33200 + PRICEREDUCTION.33200, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.35000) + s(AVGRATE.35000) + DISPLAY.35000 + PRICEREDUCTION.35000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.37000) + s(AVGRATE.37000) + DISPLAY.37000 + PRICEREDUCTION.37000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.53100) + s(AVGRATE.53100) + DISPLAY.53100 + PRICEREDUCTION.53100, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE +  s(WEEK) + s(LOYALTY.77326) + s(AVGRATE.77326) + DISPLAY.77326 + PRICEREDUCTION.77326), data=finaldata, family=multinom(K=6))

gamWeekPriceLoyaltyIModel <- gam(list(choice~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + s(WEEK) + s(LOYALTY.10158, AVGRATE.10158)+  DISPLAY.10158 +  PRICEREDUCTION.10158,  ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + ti(WEEK) +  ti(LOYALTY.33200) + ti(AVGRATE.33200) + ti(LOYALTY.33200, AVGRATE.33200) + DISPLAY.33200 + PRICEREDUCTION.33200, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + ti(WEEK) + ti(LOYALTY.35000) + ti(AVGRATE.35000) +ti(LOYALTY.35000, AVGRATE.35000) + DISPLAY.35000 + PRICEREDUCTION.35000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + ti(WEEK) + ti(LOYALTY.37000) + ti(AVGRATE.37000) + ti(LOYALTY.37000, AVGRATE.37000) + DISPLAY.37000 + PRICEREDUCTION.37000, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE + ti(WEEK) + ti(LOYALTY.53100) + ti(AVGRATE.53100) + + ti(LOYALTY.53100, AVGRATE.53100) + DISPLAY.53100 + PRICEREDUCTION.53100, ~Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE +  ti(WEEK) + ti(LOYALTY.77326) + ti(AVGRATE.77326) + ti(LOYALTY.77326, AVGRATE.77326) + DISPLAY.77326 + PRICEREDUCTION.77326), data=finaldata, family=multinom(K=6))


mlogitdata <- finaldata[,c(2, 9:46, 48)]

mlogitdata <- mlogit.data(mlogitdata, varying = c(5:39), shape = "wide", choice = "choiceLabel")
mlogitmodel <- mlogit(choiceLabel ~ 1 | Combined.Pre.Tax.Income.of.HH + MALE_SMOKE + FEM_SMOKE  + WEEK | AVGRATE + DISPLAY  + FEATURE + LOYALTY, mlogitdata, reflevel = '0')

summary(mlogitmodel)

summary(mnlmodel)
summary(gamWeekModel)
summary(gamWeekPriceLoyaltyModel)
summary(gamWeekPriceDisplaymodel)
```

